Clean spectral data

### 2021-03-05 R/clean_spectral_data.Rmd
write a cleaned spectral file before applying filtering steps and labels for classification

@@

Write spectra to csv file. 
```{r}
write_csv(x = filtered_spectra,
          path = here::here("analysis", "data", "derived_data", "cleaned_spectra.csv"))
```

>>>>

```{r write_all_cleaned_spectra}
message("# of unique taxonID values:")
length(unique(cleaned_spectra$genusSpecies))

message("# of unique scientificName values:")
length(unique(cleaned_spectra$genus))

message("# of unique spectraID (uid + year) values:")
length(unique(cleaned_spectra$spectraID))

# save this cleaned data set to a csv file 
write_csv(x = cleaned_spectra,
          path = here::here("analysis", "data", "derived_data", "cleaned_spectra.csv"))
```

@@

Write spectra to csv file. 
```{r}
write_csv(x = filtered_spectra,
          path = here::here("analysis", "data", "derived_data", "cleaned_filtered_spectra.csv"))
```
